Lattices of acyclic pipe dreams

### 2023-04-20 acyclicFacets/draft/latticePipeDreams.tex
Acknowledgements Rubey

This property is known to be true when $\omega=n\dots21$ is the reverse permutation. In this case, the increasing flip poset is the classical Tamari lattice. Removing the vertex 1 from the contact graph of a pipe dream~$P\in \pipeDreams(1\oplus \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled appropriately with the numbers from 2 to $n+1$). The edges of the binary tree are oriented going away from the root of the tree.  
We have also checked this property computationally for all dominant permutations up to $n=8$.

@@

We thank Florent Hivert for various discussions.

>>>>

This property is known to be true when $\omega=n\dots21$ is the reverse permutation. In this case, the increasing flip poset on~$\pipeDreams(1\oplus \omega)$ is the classical Tamari lattice. Removing the vertex 1 from the contact graph of a pipe dream~$P\in \pipeDreams(1\oplus \omega)$ returns the binary tree corresponding to $P$ (with the leaves removed and the internal nodes labeled appropriately with the numbers from 2 to $n+1$). The edges of the binary tree are oriented going away from the root of the tree.  
We have also checked this property computationally for all dominant permutations up to $n=8$.

@@

We are grateful to Florent Hivert for various discussions. We also thank Martin Rubey for his comments which led us to think about Open Problem~\ref{prob_nu_acyclicproperty}.
